Highlighting Disputed Claims on the Web

### 2010-02-10 papers/www_disputefinder/disputefinder_final.tex
More tweaks to address reviewer comments

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/popup_vaccine_shadow.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

One weakness of the automatic import approach is that the claims found on these sites are often phrased differently to the way they commonly appear on the web. For example many of the claims on Politifact are exact quotes such as ``One-third of the health care dollar goes to no such thing as health care; it goes to the insurance companies''. In practice, it is often necessary for users to enter several simple paraphrases for a claim before it can be reliably detected.

@@

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_disputed.png}
	\caption{Explicit page marking: select the snippet and click ``this is disputed'' on the context menu.}
	\label{mark_disputed}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/training2.png}
	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons.}
	\label{training}
	\end{center}
\end{figure}

@@

A significant weakness of the argumentation graph approach is that a good argumentation graph takes significantly more effort to build than a simple list of articles. In our prototype the argumentation graph was built entirely by users and we found that our users had difficulty creating graphs that were useful for other users. There were two problems here: first, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different opposing points; second, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}. This result is consistent with previous studies~\cite{Isenmann1997}.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/popup_graph_crop.png}
	\caption{Argumentation graph interface for a disputed claim}
	\label{popup_graph}
	\end{center}
\end{figure}

>>>>

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7.5cm]{pictures/popup_vaccine_shadow.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

One weakness of the automatic import approach is that the claims on these sites are often phrased differently to the way they commonly appear on the web. For example many of the claims on Politifact are exact quotes such as ``One-third of the health care dollar goes to no such thing as health care; it goes to the insurance companies''. In practice, it is often necessary for users to enter several simple paraphrases for a claim before it can be reliably detected.

@@

To reduce abuse, we allow a user to flag junk claims, false paraphrases, or linked articles that are not actually arguing against the disputed claim. A user should not flag a claim because they believe it is not disputed, since the level of dispute is a function of the articles that disagree. Flagging is currently moderated manually.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=5cm]{pictures/mark_disputed.png}
	\caption{Explicit page marking: select the snippet and click ``this is disputed'' on the context menu.}
	\label{mark_disputed}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/training2.png}
	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons.}
	\label{training}
	\end{center}
\end{figure}

@@

A significant weakness of the argumentation graph approach is that a good argumentation graph takes significantly more effort to build than a simple list of articles. In our prototype the argumentation graph was built entirely by users and we found that our users had difficulty creating graphs that were useful for other users. There were two problems here: first, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different points; second, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}. This result is consistent with previous studies~\cite{Isenmann1997}.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7.5cm]{pictures/popup_graph_crop.png}
	\caption{Argumentation graph interface for a disputed claim}
	\label{popup_graph}
	\end{center}
\end{figure}
